---
title: "Usage with leafletProxy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage with leafletProxy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=FALSE}
library(leaflet)
library(leaflet.multiopacity)
library(raster)

```

If you intend to use `leaflet.multiopacity` with Shiny, it is possible that you use the `leafletProxy()` function instead of only one call to `leaflet()` function. If this is your case, and you want to use the opacity controls of this package, you need to set the `renderOnLayerAdd` argument to `TRUE`. 

```{r eval=FALSE}
ui <- shiny::fluidPage(
  leaflet::leafletOutput("map"),
  shiny::actionButton("addLayers", "Add Layers")
)

server <- function(input, output, session) {
  
  # Create a map inside of your server function
  output$map <- leaflet::renderLeaflet({
    # Create raster example
    r <- raster::raster(xmn = -2.8, xmx = -2.79,
                        ymn = 54.04, ymx = 54.05,
                        nrows = 30, ncols = 30)
    raster::values(r) <- matrix(1:900, nrow(r), ncol(r), byrow = TRUE)
    raster::crs(r) <- raster::crs("+init=epsg:4326")
    
    leaflet::leaflet() %>% 
      leaflet::setView(lng = -2.79545, lat = 54.04321, zoom = 14) %>% 
      leaflet::addProviderTiles("OpenStreetMap", layerId = "osm") %>%
      leaflet.multiopacity::addOpacityControls(group = "layersToAdd", 
                                               renderOnLayerAdd = TRUE)
    
  })
  
  # Observer that trigger a map update
  shiny::observeEvent(input$addLayers, {
    leaflet::leafletProxy("map", session) %>%
      leaflet::addRasterImage(r, colors = "viridis",
                              layerId = "raster1",
                              group = "layersToAdd") %>%
      leaflet::addRasterImage(r, colors = "Spectral",
                              layerId = "raster2",
                              group = "layersToAdd") %>% 
      leaflet::addAwesomeMarkers(lng = -2.79545, lat = 54.04321, 
                                 layerId = "hospital", 
                                 label = "Hospital",
                                 group = "layersToAdd")
  })
  
}

shiny::shinyApp(ui, server)
```

Please note that you need to use this with the first `leaflet()` call, not with `leafletProxy()` call. Some leaflet plugins don't work with the current R leaflet version when called after a `leafletProxy()` call.

What the `renderOnLayerAdd` argument does, is to associate the function of creating the opacity controls to the `layerAdd` event. This way, every time a new layer is added by a `leafletProxy()` call, the controls will be updated.
