---
title: "Usage with leaflet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage with leaflet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(leaflet)
library(leaflet.multiopacity)
library(raster)
# Create raster example
r <- raster(xmn = -2.8, xmx = -2.79,
            ymn = 54.04, ymx = 54.05,
            nrows = 30, ncols = 30)
values(r) <- matrix(1:900, nrow(r), ncol(r), byrow = TRUE)
crs(r) <- CRS("+init=epsg:4326")
```

This package provides several ways to display opacity controls. The most basic usage is calling `addOpacityControls()` function without any argument.

```{r}
leaflet() %>%
  addProviderTiles("Wikimedia", layerId = "base") %>%
  addRasterImage(r, layerId = "rast") %>%
  addAwesomeMarkers(lng = -2.79545, lat = 54.04321,
                    label = "Hospital", layerId = "hospital") %>%
  addOpacityControls()
```

Note that each function call has its own layerId. If you don't provide a layerId for your layers, the opacity controls will still work, but will use the internal `_leaflet_id` as a label for each control.

You can also customize some interface aspects such as box title, position and whether opacity controls will remain collapsed.

```{r}
leaflet() %>%
  addProviderTiles("Wikimedia", layerId = "base") %>%
  addRasterImage(r, layerId = "rast") %>%
  addAwesomeMarkers(lng = -2.79545, lat = 54.04321,
                    label = "Hospital", layerId = "hospital") %>%
  addOpacityControls(collapsed = TRUE, position = "topleft")
```

You can also define the subset of layers you want to show opacity controls to. You can provide the layerId of the layers to be shown.

```{r}
leaflet() %>%
  addProviderTiles("Wikimedia", layerId = "wikimedia") %>%
  addRasterImage(r, layerId = "rast") %>%
  addAwesomeMarkers(lng = -2.79545, lat = 54.04321,
                    layerId = "hospital", label = "hospital") %>%
  addOpacityControls(layerId = c("rast", "hospital"))
```

Or the groups, if you have groups defined.

```{r}
leaflet() %>%
  addProviderTiles("Wikimedia", layerId = "wikimedia", group = "base") %>%
  addRasterImage(r, layerId = "rast", group = "rasters") %>%
  addAwesomeMarkers(lng = -2.79545, lat = 54.04321,
                    layerId = "hospital", label = "hospital",
                    group = "markers") %>%
  addOpacityControls(group = c("base", "rasters", "markers"))
```

Or even category. For example, if you want to show only rasters (category "image") or markers (category "marker"), you could specify the categories as below.

```{r}
leaflet() %>%
  addProviderTiles("Wikimedia") %>%
  addRasterImage(r, layerId = "rast") %>%
  addAwesomeMarkers(lng = -2.79545, lat = 54.04321,
                    label = "hospital", layerId = "hospital") %>%
  addOpacityControls(category = c("image", "marker"))
```
